Non-kissing and non-crossing complexes \\ for gentle algebras

### 2018-05-30 draft/accordionComplexSurfaces.tex
reduced complexes

% accordion and slalom complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
\newcommand{\edges}{\mathcal{E}} % edges of a dissection
\newcommand{\faces}{\mathcal{F}} % faces of a dissection
\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex

@@

We consider a set~$B$ of points on the boundary of the surface~$\surface$ such that~$B$ and~$M \cup M\dual$ alternate along the boundary of~$\surface$.
The points of~$B$ are called the \defn{blossom points}.
\vincent{I am tempted to define here the interior points and blossom points and to only consider arcs passing though these points. Still need to think about it.}
\end{definition}

\subsection{Accordion complex, slalom complex, and non-crossing complex}
Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points.
Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.
%Let~$I$ denote the interior points and $B$ the blossom points.

@@

\begin{definition}
\label{def:accordionComplex}
The \defn{$\dissection$-accordion complex}~$\AC$ is the simplicial complex of pairwise non-crossing $\dissection$-accordions.
\vincent{Reduced accordion complex.}
\end{definition}

@@

\begin{definition}
\label{def:slalomComplex}
The \defn{$\dissection\dual$-slalom complex}~$\SC$ is the simplicial complex of pairwise non-crossing $\dissection$-slaloms.
\vincent{Reduced slalom complex.}
\end{definition}

@@

\begin{proposition}
\label{prop:accordionsSlaloms}
For two dual cellular dissections~$\dissection$ and~$\dissection\dual$, the $\dissection$-accordions are precisely the $\dissection\dual$-slaloms and the $\dissection$-accordion complex coincides with the $\dissection\dual$-slalom complex.
\end{proposition}

@@

\begin{definition}
\label{def:noncrossingComplex}
We call \defn{non-crossing complex} of the pair of dual cellular dissections~$(\dissection, \dissection\dual)$ the simplicial complex~$\NCC = \AC = \SC$.
\end{definition}

@@

\begin{remark}
A quick disclaimer about accordion complexes and slalom complexes of arbitrary dissections, non-necessarily cellular.
As stated in Proposition~\ref{prop:conditionsDualDissections}, a dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual cellular dissection~$\dissection\dual$.
This prevents to use the definitions given in this section.
Although its accordion complex (resp.~slalom complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be join of smaller accordion complexes (resp.~slalom complexes) defined in this paper.
See \cite[Prop.~2.4]{MannevillePilaud-accordion} for a detailed statement in the case of the disk.
\end{remark}

>>>>

% accordion and slalom complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
\newcommand{\edges}{\mathcal{E}} % edges of a dissection
\newcommand{\faces}{\mathcal{F}} % faces of a dissection
\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex

@@

We consider a set~$B$ of points on the boundary of the surface~$\surface$ such that~$B$ and~$M \cup M\dual$ alternate along the boundary of~$\surface$.
The points of~$B$ are called the \defn{blossom points}.
\end{definition}

\subsection{Accordion complex, slalom complex, and non-crossing complex}
Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points.
Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.
%Let~$I$ denote the interior points and $B$ the blossom points.
We say that a $B$-arc is \defn{external} if it is homotopic to a boundary arc of~$\surface \ssm B$, and \defn{internal} otherwise.
Note that no $B$-arc can cross an external $B$-arc.

@@

\begin{definition}
\label{def:accordionComplex}
The \defn{$\dissection$-accordion complex}~$\AC$ is the simplicial complex of pairwise non-crossing $\dissection$-accordions.
The \defn{reduced $\dissection$-accordion complex}~$\RAC$ is the simplicial complex of pairwise non-crossing internal $\dissection$-accordions.
\end{definition}

@@

\begin{definition}
\label{def:slalomComplex}
The \defn{$\dissection\dual$-slalom complex}~$\SC$ is the simplicial complex of pairwise non-crossing $\dissection$-slaloms.
The \defn{reduced $\dissection\dual$-slalom complex}~$\RAC$ is the simplicial complex of pairwise non-crossing internal $\dissection\dual$-slaloms.
\end{definition}

@@

\begin{proposition}
\label{prop:accordionsSlaloms}
For two dual cellular dissections~$\dissection$ and~$\dissection\dual$, the $\dissection$-accordions are precisely the $\dissection\dual$-slaloms and the (reduced) $\dissection$-accordion complex coincides with the (reduced) $\dissection\dual$-slalom complex.
\end{proposition}

@@

\begin{definition}
\label{def:noncrossingComplex}
We call \defn{non-crossing complex} of the pair of dual cellular dissections~$(\dissection, \dissection\dual)$ the simplicial complex~$\NCC = \AC = \SC$.
Similarly, the \defn{reduced non-crossing complex} of~$(\dissection, \dissection\dual)$ is~$\RNCC = \RAC = \RAC$.
\end{definition}

@@

\begin{remark}
A quick disclaimer about accordion complexes and slalom complexes of arbitrary dissections.
As stated in Proposition~\ref{prop:conditionsDualDissections}, a dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual cellular dissection~$\dissection\dual$.
This prevents to use the definitions given in this section.
Although its accordion complex (resp.~slalom complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be join of smaller accordion complexes (resp.~slalom complexes) defined in this paper.
See \cite[Prop.~2.4]{MannevillePilaud-accordion} for a detailed statement in the case of the disk.
\vincent{A retravailler}
\end{remark}
